---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pmapply

![](https://camo.githubusercontent.com/ea6e0ff99602c3563e3dd684abf60b30edceaeef/68747470733a2f2f696d672e736869656c64732e696f2f62616467652f6c6966656379636c652d6578706572696d656e74616c2d6f72616e67652e737667)
<!-- badges: end -->

The goal of pmapply is to apply a pair-wise function over a series of vectors. 

## Installation

You can install the released version of pmapply from GitHub with:

``` r
remotes::install_github("daranzolin/pmapply")
```

## Example: What keys should I use to join my tables?

Suppose you have several tables with varying keys. Some may match, some may partially match, and some may not match at all. Rather than rerunning `sum(key1 %in% key2)`, `sum(key2 %in% key3)`, `sum(key1 %in% key3)` *ad infinitum*, use `pmapply`:


```{r}
library(pmapply)

generate_keys <- function(n = 1200) {
  a <- do.call(paste0, replicate(5, sample(LETTERS, n, TRUE), FALSE))
  paste0(a, sprintf("%04d", sample(9999, n, TRUE)), sample(LETTERS, n, TRUE))
}
keys <- generate_keys()
l <- list(
  k1 = sample(keys, 1000),
  k2 = sample(keys, 1000),
  k3 = sample(keys, 1000),
  k4 = sample(keys, 1000)
)

si <- function(x, y) sum(x %in% y)
m <- pmapply(l, si)
m
```

The resulting matrix shows the total intersections between each combination.

Get the minimum and maximum values with `get_min_max_combos`:

```{r}
get_minmax_combos(m)
```

Or plot the heatmap with `combo_heatmap`:

```{r}
combo_heatmap(m)
```

## Example 2: Correlation Matrices

```{r}
(cormat <- pmapply(iris[,c(1:4)], function(x, y) cor(x, y)))
combo_heatmap(cormat)
```


